Git Learning Notes

### 2014-09-06 BackMatter/app3.tex
ch2 and appendix update

\chapter{Processes developed during Ph.D. study}

\section{Growth recipes}

@@

>>>>

%\chapter{Processes developed during Ph.D. study}
\chapter{Growth Recipes}

A schematic diagram of the home-built CVD system is shown in Fig.~\ref{fig:ch2cvd}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{CVD_model.jpg}
\caption{Sketch of CVD system for oxide growth, where A1: quartz tube; B1: bubbler; C1-2: gas cylinders; E1: mechanical pump; H1-2: ceramic heater; MFC: flow controller; P1: pressure gauge; V1-4: valves; V5-7: butterfly valves. Note: the thermal sensor attached on H-1 is not shown. }
\label{fig:ch2cvd}
\end{figure}

The following text will refer to this diagram using \fbox{symbol in box} when a specific component is mentioned. Please note that the actual CVD system is subject to changes, \emph{e.g.}, in the sulfurization system, a cold trap is used and oxygen tank is absent; whereas in the ZnTe system, a pressure controller is added and hydrogen instead of oxygen is used.

\section{Basic Operation}
Before performing growth, check the CVD system to confirm its normal state, where the vacuum in idle status is manifested as:
\begin{itemize}
\item 5-7 mTorr reading for the pressure gauge (\fbox{P-1})of ZnTe CVD;
\item 20-22 mTorr reading for the pressure gauge (\fbox{P-1})of oxide CVD;
\item 45-50 mTorr reading for the pressure gauge (\fbox{P-1}) of sulfur CVD. 
\end{itemize} 
and the mass flow controller reading (\fbox{MFC}) should be either negative or zero. If large deviation occurs, check the vacuum sealing and report to lab manager.

\subsection{Venting the chamber}
To load/unload sample into/out of the chamber, one first needs to bring the pressure up to 1 atm. This is done by purging the chamber using Ar gas using steps as following (\textbf{FOLLOW THE EXACT ORDER}):
\begin{enumerate}
\item close \fbox{V-5}, one should observe \fbox{P-1} reading increases;
\item toggle Ar gas switch from OFF to ON, wait for 10 s;
\item toggle Ar gas purge switch, watching \fbox{P-1} closely; When the chamber is purged with Ar, the indications of actual pressure reaching 1 atm inside are shown as: 
\begin{itemize}
\item 760 Torr reading for the ZnTe CVD;
\item 32-33 Torr reading for the oxide CVD;
\item 24 Torr reading for the sulfur CVD. 
\end{itemize} \textbf{Avoid} using higher venting pressure. 
\item Turn off Ar purge switch rapidly when 1 atm is reached; 
\item Slowly open \fbox{V-4} to test the ``water'' level in \fbox{B-1}. Close \fbox{V-4} if the level goes up; fully open \fbox{V-4} if otherwise. 
\end{enumerate}
%Using the same procedure when harvesting the samples.

\subsection{Pumping down the chamber}
Most of synthesis experiments in this group are performed in low pressure conditions, so after loading the substrate and source, one needs to pump down the system using the following steps (\textbf{FOLLOW THE EXACT ORDER}):
\begin{enumerate}
\item seal the chamber and keep the Ar flow on, one should observe continuous bubbling in \fbox{B-1}. If not check the vacuum sealing;
\item turn off ANY gas flow first, then close \fbox{V-4};
\item open \fbox{V-5} slowly, check \fbox{P-1} reading, which should drop rapidly to similar value as in idle status. If not, STOP and check the vacuum sealing.  
\end{enumerate}

\subsection{Starting heating} 
The heating is controlled by a close-loop PID method, with the control panel shown in Fig.~\ref{fig:omega}. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{omega_temp}
\caption{Front panel of temperature controller, and the four keys are denoted as $\Omega$, $\nabla$, $\Delta$, and $\Xi$ here. SV means setting value; PV means present value.}
\label{fig:omega}
\end{figure}

Change to heating mode by the following steps:
\begin{enumerate}
\item turn on the voltage transformer; 
\item hold $\Xi$ key for 3 second;
\item use $\nabla$ or $\Delta$ key to circle until ``r.s'' emerges;
\item hold $\Xi$ key for 1 second to confirm.
\end{enumerate}

\textcolor{red}{Check the CVD system status periodically, and update the default status. \textbf{DO NOT} proceed if in question. Consult the lab manager or supervisor.}

\section{Emergence Procedures}

When the temperature controller is recovered from a power outrage event, it will try to resume the previous heating procedure or start the stored procedure. This can be a problem depending on the previous CVD system status. Therefore, it is required that the temperature controller is put to standby mode manually by the frequent user.

Change to standby mode by the following steps:
\begin{enumerate}
\item turn off the voltage transformer; 
\item hold $\Xi$ key for 3 second;
\item use $\nabla$ or $\Delta$ key to circle until ``stby'' emerges;
\item hold $\Xi$ key for 1 second to confirm.
\end{enumerate}

\newpage
%\section{Growth Recipes}

\section{Substrates and Precursors}

The precursors are summarized in Table.~\ref{tb:pre} and Table.~\ref{tb:mosource}, and substrates in Table.~\ref{tb:subs}.

\begin{table}[htb]
\centering
\caption{List of reactants:\ce{WO3},\ce{WS2}}\label{tb:pre}
\begin{tabular}{lcccr}
\toprule
Materials & Name & Purity & Average size & Vendor LOT\\
\midrule
Tungsten & 3N   &  99.9\% & 17 $\mu$m & Alfa Aesar \#39749\\
         & 3N5  &  99.95\% & 32 $\mu$m  & Alfa Aesar \#42477\\
         & 4N5  &  99.995\% & 3.3 $\mu$m  & Materion T-2049 \\
         & 5N   &  99.999\% & 1.5 $\mu$m & Alfa Aesar \#12973\\
Sulfur   & S    &   99.5\%  &  NA  & Alfa Aesar \#10785\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[htb]
\centering
\caption{List of reactants: \ce{MoO3}}\label{tb:mosource}
\begin{tabular}{lcccr}
\toprule
Material & Stock No & LOT &Purity & Vendor\\
\midrule
\ce{NaOH}        & S318-500 & 070241 & 99.8\% & Fisher Scientific \\
\ce{NaI}        & 11665 & K11W054 & 99.9\% &  Alfa Aesar \\
\ce{KI}        & 42857 & H06Z051 & 99.9\% &  Alfa Aesar \\
\ce{Na2CO3}        & 33377 & 114X012 & 99.95\% &  Alfa Aesar \\
\ce{Molybdenum}        & 00932 & I07S024 & 99.9\% &  Alfa Aesar\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[htb]
\centering
\caption{List of substrates}\label{tb:subs}
\begin{tabular}{lcp{3in}}
\toprule
Name & Resistivity (\si{\ohm cm}) &  Remark\\
\midrule
\ce{SiO2}-Si  & 0.06 - 0.12  & p type, Born, (100), 1 $\mu$m thermally grown \ce{SiO2} \\
\ce{SiO2}-Si  & 1 - 10       & p type, Born, (100), 300 nm thermally grown \ce{SiO2} \\
\ce{Si}       & 3 - 7        & n type, Phosporus (100) \\
Glass         & NA           &  microscope slide\\
ITO glass     &               & \ce{SiO2} passivated, 1.1 mm thick float glass \\
Mica          & NA            & \ce{K(Al2)(Si3Al)O10(OH)2} \\
\bottomrule
\end{tabular}
\end{table}

\section{Tungsten Oxides Growth}
\subsection{Seeded Growth}

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{wo3_seed}
\caption{Seed \ce{WO3} growth setup, the symbols meaning are explained in Table.~\ref{tb:pre}}
\label{fig:seed}
\end{figure}

The substrate treatment in the seeded growth only includes usual cleaning using organic solvents. The growth steps are as following:

\begin{enumerate}
\item Load $\sim$1 g high purity W powder into the handler end of the long boat, spread the power evenly into 1 in long;  
\item Load a thin layer of 3N W powder on the clean substrate, spread them uniformly by putting the polished side of another clean Si substrate against the power and sliding the top substrate gently; 
\item Position the substrate with W powder into the same long boat in a way that when the whole boat in loaded into the chamber, the separation between substrate and power source is the same as indicated in Fig.~\ref{fig:seed};
\item Vent the chamber to 1 atm, load the long boat with the substrate and source as shown in Fig.~\ref{fig:seed};
\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
\item Admit gases (10 sccm Ar and 0.3 sccm \ce{O2}) into the chamber, record the corresponding pressure reading;
\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:seed}; 
\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
\item Put up the warning sign beside the furnace;
\end{enumerate}

\subsection{NaOH-Si Growth}

The substrate treatment in this growth includes \begin{enumerate*}[label=\itshape\alph*\upshape)]
\item usual cleaning using organic solvents;
\item plasma cleaning (2 Torr oxygen, 3 min); and
\item drop casting of NaOH solution (50 $\mu$L, 0.01 mol/L).
\end{enumerate*} The growth steps are as following:

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{wo3_naoh}
\caption{NaOH \ce{WO3} growth, the symbols meaning are explained in Table.~\ref{tb:pre}}
\label{fig:naw}
\end{figure}

\begin{enumerate}
\item Load $\sim$1 g high purity W powder into the handler end of the long boat, spread the power evenly into 1 in long;
\item Position the NaOH--treated substrate into the same long boat in a way that when the whole boat in loaded into the chamber, the separation between substrate and power source is the same as indicated in Fig.~\ref{fig:naw};
\item Vent the chamber to 1 atm, load the long boat with the substrate and source as shown in Fig.~\ref{fig:naw};
\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
\item Admit gases (10 sccm Ar and 0.4 sccm \ce{O2}) into the chamber, record the corresponding pressure reading;
\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:naw}; 
\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
\item Put up the warning sign beside the furnace;
\end{enumerate}

\section{Sulfurization}

The as-synthesized \ce{WO3} samples are further sulfurized to fabricate the core-shell heterostructure.

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_coreshell}
\caption{\ce{WO3} sulfurization growth}
\label{fig:suf}
\end{figure}

\begin{enumerate}
\item Prepare 200 -- 300 g Sulfur in a small boat;
\item Vent the chamber to 1 atm, and position the as-grown \ce{WO3} sample and small boat with S into chamber as indicated in Fig.~\ref{fig:suf};
\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
\item Add liquid nitrogen into cold trap; 
\item Admit gases (30 sccm Ar) into the chamber, record the corresponding pressure reading;
\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:suf}; 
\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
\item Put up the warning sign beside the furnace;
\end{enumerate}

\section{Moly Oxide Growth}

The substrate treatment in this growth includes \begin{enumerate*}[label=\itshape\alph*\upshape)]
\item usual cleaning using organic solvents;
\item plasma cleaning (2 Torr oxygen, 3 min); and
\item drop casting of NaOH solution (50 $\mu$L, 0.01 mol/L).
\end{enumerate*} The growth steps are as following:

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{moo3_naoh}
\caption{NaOH \ce{MoO3} growth}
\label{fig:namo}
\end{figure}

\begin{enumerate}
\item Load $\sim$1 g Mo powder into the handler end of the long boat, spread the power evenly into 1 in long;
\item Position the NaOH--treated substrate into the same long boat in a way that when the whole boat in loaded into the chamber, the separation between substrate and power source is the same as indicated in Fig.~\ref{fig:namo};
\item Vent the chamber to 1 atm (32-33 Torr reading on gauge), load the long boat with the substrate and source as shown in Fig.~\ref{fig:namo};
\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
\item Admit gases (10 sccm Ar and 10 sccm \ce{O2}) into the chamber, record the corresponding pressure reading;
\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:namo}; 
\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
\item Put up the warning sign beside the furnace;
\end{enumerate}

\iffalse

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{omega_temp}
\caption{Front panel of temperature controller, and the four keys are denoted as $\Omega$, $\nabla$, $\Delta$, and $\Xi$ here. SV means setting value; PV means present value.}
\label{fig:omega}
\end{figure}

Change heating procedure ( heating time and temperature) by the following steps:
\begin{enumerate}
\item hold $\Omega$ key for 3 second; a new display should show up, 
\item use $Xi$ key to circle until ``r.s'' emerges;
\item hold $\Xi$ key for 1 second to confirm.
\end{enumerate}

\subsection{sulfurization}

@@

\fi

### 2014-09-06 BackMatter/paper.tex
ch2 and appendix update

@@

>>>>

why graphene on copper: a review article. \cite{Mattevi2011} research thrust, post CMOS fab tech. Exposure of hydrocarbon or evaporated carbon onto transition metal, the formation of graphite was surmised as a consequence of diffusion and segregation of carbon impurities from bulk to surface. carbon solubility in the metal and.

The lack of control over layer No on Ni is partially attributed to the face that the segregation of carbon from the metal carbide upon cooling occurs rapidly within the Ni grains and heterogeneously at the grain boundaries. phase diagram of Ni and C reveals that the solubility of carbon in nickel at high T > 800 C form a solid solution. metastable phase \ce{Ni3C} promote the precipitation of C out of Ni. Carbon preferentially precipitates out at the grain boundaries of polycrystalline Ni subs so the thickness at graphite is higher than within grains. On Fe, due to the high affinity between Fe and C (\ce{Fe3C} is a stable carbide), the formation of $sp^2$ crystalline carbon film is suppressed.

on copper (decomposition of methane gas at 1100 C), independent of heating or cooling rate. For copper, the 3d shell is filled, leading to less reactive configuration and weaker affinity towards Carbon. Cu can only form soft bonds with C via the charge transfer from the $\pi$ electron in  sp2 hybridized C to the empty 4s states of copper, as supported by the fact that copper does not form any carbide phase, and low C solubility. This low affinity and weak bond makes copper a true catalyst fro graphitic carbon formation. pre-treatment of copper foil, \ce{CuO}, \ce{Cu2O} removal by reducing annealing at 1000 C.

epitaxial and lattice mismatch is present,

\textbf{four-point probe}

sheet resistivity. a current source in an infinite sheet gives rise to the logarithmic potential
\[
\phi - \phi_0 = - \frac{I\rho}{2\pi}\log r,
\]
the potential for a dipole becomes
\[
\phi - \phi_0 = \frac{I\rho}{2\pi}\log r_1/r_2,
\]

When equal spacing probes are used, then potential difference between two inner points is 
\[
\delta\phi = V = \frac{I \rho}{\pi}\log2,
\]
so sheet resistivity $\rho$ is obtained as
\[
\rho = 4.5324V/I.
\]

@@

\section{Gary semiconductor fabrication}

photolithography a patter transferring process from mask to photoresist. clean room needed to remove dust particles, which could cause dislocation on an epitaxial film, low breakdown voltage in gate oxide, or short circuit.

resolution, registration for effectiveness, throughput for efficiency, shadow printing where mask and wafer in direct contact: cons, dust could case permanent damage to mask, a small gap $d$ (10-50 $\mu$m ) used usually, and the minimium linewideth CD is roughly $\sqrt{\lambda d}$; and projection printing , resolution $l_m = \frac{k_1 \lambda}{NA}$, and depth of focus $\frac{k_2 \lambda}{NA^2}$. 193-nm using ArF excimer laser, and 157 nm using \ce{F2} excimer laser.

365 nm probably used for \ce{LiNbO3} waveguide.

resolution enhancement using phase shifting mask,  using the electric field of EM wave to chemically activate the photoresist. A $\pi$ phase change is obtained by using a transparent layer of $d = \lambda/2(n - 1)$ thickness. near-field diffraction,

EUV 10 - 14 nm, C inner shell electron transition,

\section{non-imaging optics}

black body radiation power density $S$ is about 1 \si{kW\per m^2}, the balanced temperature $T = \sqrt[4]{S/\sigma} = 364$ K, where $\sigma$ is Stefan-Boltzmann constant.

ray tracing in vector form as $n^{\prime} r^{\prime} \times n = n r \times n$, invariant $na\theta$,

### 2014-09-06 ch-intro/ch-instr.tex
ch2 and appendix update

Diffuse reflection spectroscopy (DRS) serves as another tool to estimate the sample band gap using Kubelka-Munk theory (KM).\cite{Tandon1970} The original KM theory was proposed in 1931,\cite{Kubelka1931} and has been popular in the color-related industry, such as painting, pigments, and paper. Some key points were recapitulated in this thesis.

@@

@@

with the aid of Fig.

>>>>

Diffuse reflection spectroscopy (DRS) serves as another tool to estimate the sample band gap using Kubelka-Munk theory (KM).\cite{Tandon1970} The original KM theory was proposed in 1931,\cite{Kubelka1931} and has been popular in the color-related industry, such as painting, pigments, and paper. This method is useful for the analysis of samples of difficultly soluble substances and for samples that will react with the solvents upon being dissolved. It is also particularly applicable when single crystals of the material could not be obtained. Some key points were recapitulated in this thesis.

@@

the reflecting power associated with a specular-type process is often termed reflectivity, while reflectance is the analogous term for diffusely reflected radiation. This two types of reflection are present simultaneously.

Cauchy formula, empirical equation which has subsequently been placed on a firm theoretical basis.

intensity for a complex quantities is obtained by multiplying the complex conjugate.

For strongly absorbing materials, the reflected light is complementary to the color of light transmitted by it, such as gold transmission is green;

For the weakly absorbing substances of rough surface, it will appear the same color by transmission or reflection.

penetration depth is wavelength dependent $d = \frac{In2 \lambda}{2\pi \sqrt{\sin^2\theta_i - n^2}}$, longer wavelength penetrated further than did shorter wavelength. attenuated total reflectance,

thin film, amorphous, mean free path of electron is diminished, and porous in structure. The maxwell-garnett theory provides a satisfactory explanation, where free electron density is reduced.

diffuse reflection: $I = I_0 \exp(-\epsilon d)$, Lambert cosine law formulated. multiple scattering by individual particles. 
$R_tot = \alpha R_sp + (1- \alpha) R_diff $,

multiple scattering of diffuse radiation in a medium composed of closely packed particles.

\[
\log{f(r_\infty) = \log{k} - \log{s}}
\]

It is concluded that the KM function can be used to obtain the characteristic color curve of a given sample only in the limit of small total absorption.

by mixing the sample with an abundance of the reflectance standard, the regular reflection is extensively eliminated.

The color of an object depends on the spectral composition of the source. The color of many light sources can be specified in terms of the temperature to which a blackbody radiator must be heated in order to achieve a color match for the source, which is known as color temperature.

integrating sphere: the intensity at any part of the sphere, due to the reflected light is a measure of the total flux from a particular source, independent of the spatial distribution or location of the source on the sphere.

substitution method, comparison method,

@@

The information about an object is on display in the objective lens's back focal plane in a Fourier-transform form. dark field, removing zero order; Schlieren technique, removing half of diffraction from one side of back focal plane; applications: apodizing in telescope, satellite transmitting aerial structure,

with the aid of Fig. 
conjugate plane,

electron lens can be made of electrostatic field, and magnetic field, and the B field can be generated from ferromagnetic materials (soft iron, 2 T) or superconducting (100 T).

$C_s$ has dimensions of length, and is approximately equal to the focal length of objective lens (1-3 mm in TEM).

$r_{min} \approx 0.91(C_s \lambda^3)^{1/4}$ is about 0.3 nm typically; with $C_s$ correction, $r_{min}$ can be further reduced to 0.07 nm. And human eye can resolve a distance of 0.2 mm, therefore the maximum useful magnification is about $0.2 \times 10^{-3}/0.3 \times 10^{-9} \sim 670 K$.

And after interacting with specimen, the energy spread of transmitted E-beam becomes about 20eV, which will limit the resolution more than does the spherical aberration.

\textbf{coherence of E-beam}

faint points, large disk, the feature of interest is what make the materials imperfect,

20 keV E-beam in TV.

In XRD, both diffraction peak position and intensity are used; whereas in TEM, most time only the positions of spots are of concern.

physical process of diffraction where the atomic planes appear to behave as mirrors for incident E-beam;
